Containers and R---the Rockerverse and beyond

### 2019-11-06 manuscript.Rmd
Update style file and don't add extra packages for ORCiD while still following ORCID display guidelines
See also https://orcid.org/trademark-and-id-display-guidelines and https://journal.r-project.org/share/author-guide.pdf

---
title: "Containers and R---the Rockerverse and beyond"
author:
  - name: Daniel Nüst
    affiliation: Institute for Geoinformatics, University of Münster
    address:
    - Heisenbergstr. 2
    - 48149 Münster
    - Germany
    - \orcid{0000-0002-0024-5046}
    email: daniel.nuest@uni-muenster.de
  - name: Carl Boettiger
    #affiliation: -
    #email: -
  - name: Robrecht Cannoodt
    #affiliatin: -
    #email: -
  - name: Dirk Eddelbuettel
    affiliation: University of Illinois at Urbana-Champaign
    address:
      - Department of Statistics
      - Illini Hall, 725 S Wright St
      - Champaign, IL 61820
      - \orcid{0000-0001-6419-907X}
    email: dirkd@eddelbuettel.com
  - name: Mark Edmondson
    affiliation: IIH Nordic A/S, Google Developer Expert for GCP
    email: mark@markedmondson.me
  - name: Colin Fay
    affiliation: ThinkR
    email: contact@colinfay.me
  - name: Ben Marwick
    #affiliation: -
    #email: -
  - name: Karthik Ram
    #affiliation: -
    #email: -
  - name: Noam Ross
    #affiliation: -
    #email: -
  - name: Nan Xiao
    affiliation: Seven Bridges Genomics
    address:
      - 529 Main St, Suite 6610
      - Charlestown, MA 02129, USA
      - \orcid{0000-0002-0250-5673}
    email: me@nanx.me
  - name: Lori Shepherd
    affiliation: Roswell Park Comprehensive Cancer Center
    address:
      - Elm & Carlton Streets
      - Buffalo, New York, 14263 USA
      - \orcid{0000-0002-5910-4010}
    email: lori.shepherd@roswellpark.org
  - name: Nitesh Turaga
    affiliation: Roswell Park Comprehensive Cancer Center
    address:
    - Elm & Carlton Streets
    - Buffalo, New York, 14263 USA
    - \orcid{0000-0002-0224-9817}
    email: nitesh.turaga@roswellpark.org
abstract: >
  The Rocker project provides widely-used Docker images for R across different application scenarios.
  This articles surveys describe downstream projects building upon Rocker.
  We also look beyond Rocker to other projects connecting containerisation with R.
  These use cases and the diversity of applications demonstrate the power of Rocker and containerisation for collaboration, effectivity, scalability, and transparency.
# blank footnote? https://tex.stackexchange.com/questions/170511/footnotes-without-numbering
output:
  rticles::rjournal_article:
    keep_tex: true
---

@@

DN conceived of the presented idea and \href{https://github.com/nuest/rockerverse-paper/issues/3}{initialised the formation of the writing team}.
CB ..
RC ..
DE ..
ME ..
CF ..
BW ..
KR ..
NR ..
NX wrote the section on liftr.
LS \& NT wrote the section on Bioconductor.
All authors contributed to the discussion and outlook section and approved the final version.
This articles was collaboratively written at \href{https://github.com/nuest/rockerverse-paper/}{https://github.com/nuest/rockerverse-paper/}.
The \href{https://github.com/nuest/rockerverse-paper/graphs/contributors}{contributors page} and \href{https://github.com/nuest/rockerverse-paper/commits/master}{commit history} provide a detailed view on the respective contributions.

>>>>

---
title: "Containers and R---the Rockerverse and beyond"
author:
  - name: Daniel Nüst
    affiliation: Institute for Geoinformatics, University of Münster
    address:
    - Heisenbergstr. 2
    - 48149 Münster
    - Germany
    - \href{https://orcid.org/0000-0002-0024-5046}{\includegraphics[height=\fontcharht\font`\0]{ORCID-iD_icon-vector.pdf} https://orcid.org/0000-0002-0024-5046}
    email: daniel.nuest@uni-muenster.de
  - name: Carl Boettiger
    #affiliation: -
    #email: -
  - name: Robrecht Cannoodt
    #affiliatin: -
    #email: -
  - name: Dirk Eddelbuettel
    affiliation: University of Illinois at Urbana-Champaign
    address:
      - Department of Statistics
      - Illini Hall, 725 S Wright St
      - Champaign, IL 61820
      - \includegraphics[height=\fontcharht\font`\0]{ORCID-iD_icon-vector.pdf} \href{https://orcid.org/0000-0001-6419-907X}{https://orcid.org/0000-0001-6419-907X}
    email: dirkd@eddelbuettel.com
  - name: Mark Edmondson
    affiliation: IIH Nordic A/S, Google Developer Expert for GCP
    email: mark@markedmondson.me
  - name: Colin Fay
    affiliation: ThinkR
    email: contact@colinfay.me
  - name: Ben Marwick
    #affiliation: -
    #email: -
  - name: Karthik Ram
    #affiliation: -
    #email: -
  - name: Noam Ross
    #affiliation: -
    #email: -
  - name: Nan Xiao
    affiliation: Seven Bridges Genomics
    address:
      - 529 Main St, Suite 6610
      - Charlestown, MA 02129, USA
      - \includegraphics[height=\fontcharht\font`\0]{ORCID-iD_icon-vector.pdf} \href{https://orcid.org/0000-0002-0250-5673}{https://orcid.org/0000-0002-0250-5673}
    email: me@nanx.me
  - name: Lori Shepherd
    affiliation: Roswell Park Comprehensive Cancer Center
    address:
      - Elm & Carlton Streets
      - Buffalo, New York, 14263 USA
      - \includegraphics[height=\fontcharht\font`\0]{ORCID-iD_icon-vector.pdf} \href{https://orcid.org/0000-0002-5910-4010}{https://orcid.org/0000-0002-5910-4010}
    email: lori.shepherd@roswellpark.org
  - name: Nitesh Turaga
    affiliation: Roswell Park Comprehensive Cancer Center
    address:
    - Elm & Carlton Streets
    - Buffalo, New York, 14263 USA
    - \includegraphics[height=\fontcharht\font`\0]{ORCID-iD_icon-vector.pdf} \href{https://orcid.org/0000-0002-0224-9817}{https://orcid.org/0000-0002-0224-9817}
    email: nitesh.turaga@roswellpark.org
abstract: >
  The Rocker project provides widely-used Docker images for R across different application scenarios.
  This articles surveys describe downstream projects building upon Rocker.
  We also look beyond Rocker to other projects connecting containerisation with R.
  These use cases and the diversity of applications demonstrate the power of Rocker and containerisation for collaboration, effectivity, scalability, and transparency.
# blank footnote? https://tex.stackexchange.com/questions/170511/footnotes-without-numbering
output:
  rticles::rjournal_article:
    keep_tex: true
---

@@

DN conceived of the presented idea and \href{https://github.com/nuest/rockerverse-paper/issues/3}{initialised the formation of the writing team}.
CB ..
RC ..
DE ..
ME ..
CF wrote the section about `r-online`, `dockerfiler`, `r-ci` and `r-db`.
BW ..
KR ..
NR ..
NX wrote the section on liftr.
LS \& NT wrote the section on Bioconductor.
All authors contributed to the discussion and outlook section and approved the final version.
This articles was collaboratively written at \href{https://github.com/nuest/rockerverse-paper/}{https://github.com/nuest/rockerverse-paper/}.
The \href{https://github.com/nuest/rockerverse-paper/graphs/contributors}{contributors page} and \href{https://github.com/nuest/rockerverse-paper/commits/master}{commit history} provide a detailed view on the respective contributions.
